%-------------------------
% Resume in Latex
% Adapted for Dasari Hemavathi
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage[scale=0.90,lf]{FiraMono}
\usepackage{contour}
\usepackage[normalem]{ulem}
\usepackage{tgheros}
\usepackage[T1]{fontenc}

\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\renewcommand{\ULdepth}{1.8pt}
\contourlength{0.8pt}
\newcommand{\myuline}[1]{%
  \uline{\phantom{#1}}%
  \llap{\contour{white}{#1}}%
}

\renewcommand*\familydefault{\sfdefault}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

\newcommand{\resumeItem}[1]{
  \item\small{{#1 \vspace{-1pt}}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\
      \textit{#3} & {\color{dark-grey} \small #4}\\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey} #2} \\
    \end{tabular*}\vspace{-4pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\color{text-grey}

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Dasari Hemavathi} \\ \vspace{5pt}
    \small \faPhone* \texttt{+91 8309854507} \hspace{1pt} $|$
    \hspace{1pt} \faEnvelope \hspace{2pt} \texttt{hemadasari137@gmail.com} \hspace{1pt} $|$
    \hspace{1pt} \faLinkedin \hspace{2pt} \href{https://linkedin.com/in/dasarihemavathi}{\texttt{linkedin.com/in/dasarihemavathi}} \hspace{1pt} $|$
    \hspace{1pt} \faGithub \hspace{2pt} \href{https://github.com/Dasarihemavathi}{\texttt{github.com/Dasarihemavathi}} \\
    \vspace{2pt}
    \small \faMapMarker* \hspace{2pt}\texttt{Bengaluru, BTM Layout}
\end{center}

%-----------CAREER OBJECTIVE-----------
\section{CAREER OBJECTIVE}
\small
Motivated Full Stack Developer seeking IT roles related to Python, Django, Frontend Development, and MySQL. I aim to contribute by building clean, user-friendly, and reliable web applications while continuously improving through real-world development work.

%-----------PROJECTS-----------
\section{PROJECTS}
\resumeSubHeadingListStart

\resumeProjectHeading
  {\textbf{Smart Task Manager} $|$ \emph{React, Python, Django, MySQL}}{}
  \resumeItemListStart
    \resumeItem{Built a task management application with authentication, due-date tracking, and productivity dashboard features.}
    \resumeItem{Implemented full CRUD operations with structured backend APIs and database integration.}
    \resumeItem{Focused on reusable UI components and clean project architecture for maintainability.}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{Student Course API} $|$ \emph{Python, Django, MySQL, REST API}}{}
  \resumeItemListStart
    \resumeItem{Designed REST APIs for course enrollment, progress tracking, and admin-side operations.}
    \resumeItem{Added authentication and role-based access controls for secure API usage.}
    \resumeItem{Improved data handling with validation and clear endpoint structure.}
  \resumeItemListEnd

\resumeProjectHeading
  {\textbf{Classic Snake Game} $|$ \emph{JavaScript, Python, HTML/CSS}}{}
  \resumeItemListStart
    \resumeItem{Developed a browser-based Snake game with score tracking and leaderboard functionality.}
    \resumeItem{Integrated game frontend with backend APIs for persistent score storage.}
    \resumeItem{Implemented restart flow, keyboard controls, and responsive UI behavior.}
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{EDUCATION}
\resumeSubHeadingListStart

\resumeSubheading
  {Krishna Chaitanya Institute of Technology and Sciences}{Markapur, Andhra Pradesh}
  {B.Tech in Computer Science and Engineering}{CGPA: 8.68}

\resumeSubheading
  {KGBV School}{Rajupalem}
  {Intermediate (MPC)}{CGPA: 7.9}

\resumeSubheading
  {KGBV Rajupalem}{Rajupalem}
  {SSC}{CGPA: 9.7}

\resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{SKILLS}
\begin{itemize}[leftmargin=0in, label={}]
\small{\item{
\textbf{Frontend} {: HTML5, CSS3, JavaScript, React, Responsive Design} \\
\textbf{Backend} {: Python, Django, REST APIs, Authentication} \\
\textbf{Database} {: MySQL, SQL} \\
\textbf{Tools} {: Git, GitHub, VS Code, Cursor, Codex, Postman}
}}
\end{itemize}

\end{document}